% -*- mode: TeX -*-
% -*- coding: utf-8 -*-

About 5 years ago I landed in Stockholm at the very beginning of October with some 
idea of doing this thing called Ph.D. --- \emph{Philosophiae Doctor}. Back then, 
I did not know what kind of future I had ahead of me --- and still is a work in 
progress --- but over time I understood that you make your own future. You take 
full credit for your successes and your mistakes, sometimes on your own, and some 
other times in collaboration with others.

Now it is the time to say thank you, a thank you that honestly feels quite short 
and vague because I do not think that it is possible to describe it in words. Most 
likely Miguel de Cervantes Saavedra --- a prolific Spanish writer and father of the first 
modern novel known as Don Quijote  de la Mancha --- was one of the very few writers 
in the world who could actually put words to such feeling.

And here it comes... first, and foremost, I have to thank my advisor, Sonja, whom 
I have shared uncountable hours talking and discussing our daily work, and also 
quite some other amount arguing. I have to admit that my Southern Europeanness --- whom I am 
and will always be very proud of --- mixed quite abruptly with a Northern Europeanness 
that I fought --- unsubsconsciously --- for a very long while. And despite my complaints 
(not to her though :) I understood those little details that now are part of me 
and actually I kind of like --- some may see as a factor for Stockholm's syndrom :).
Some say an advisor is like a father (or a mother for that matter) and I agree up 

Thanks to my co-authors --- in no particular order --- Benny, Oleksandr, Gunnar, 
Tomas and Sonja. 

I also owe my strength to continue on this path to that woman who never gave up 
and fought till the last breath. She inspired me on this path and every time I saw 
her she would just smile and be happy to me and while I was away she would always 
ask for me. Unfortunately, she did not get the chance to see with her eyes this 
book finished. Wherever you are, I miss you grandma.

Parents... 

These years I have shared different offices --- not one... nor two... but three! 
--- with quite some people. The first few years before we were moved one floor up 
I spent some quality time with Torbjörn, Mussard and Benny, each one putting that 
little bit of spice to the lively environment we had. Then, after the move, I joined 
Siavash in that tiny office that regardless of the minimal space we manage to make 
it feel spacious enough. Siavash and me had great conversations about everything.
Though when he finished his degree... I was kind of forced to move as well to the 
room next door, at first, disliking the idea of getting more space but later on... 
enjoying the German environment with Benny and Oliver.

Interestingly enough, each one managed to Benny and Oliver are quite opposite when it comes to personality 

With Oliver I have had 
so many conversations --- and also jokes about the German way of doing things... --- 
that I can't count.

At the department there have been many other people. Some passing by shortly, and 
some others still enjoying --- or suffering, depends on the interpretation :). Among 
those, all the other Ph.D students 

Last, but not least, Joshua is that guy who has taken my desperation --- or happiness... 
again, interpretations :) --- and the joyful moments as well the past few years. 
Somehow it feels like apologising because he has taken most of my anger quite happily.

Another acknowledgement goes to our little cat, Barney. A long black smoke sausage --- 
I did not imagine cats could compete in length with these long sausage dogs :) --- 
whom miaus in between has suffered some of my sleepless writing nights and he always 
managed to get me to smile and stop for after his smelling practices.

Finally --- and a warning to the random reader, these acknowledgements are, by no 
means, complete. They are a work in progress and they will be updated --- or enhanced ---
in the next iteration. I believe the name is called actually doctoral thesis. See 
you soon.

"If something is important enough, even if the odds are against you, you should still do it."
"Persistence is very important. You should not give up unless you are forced to give up."

Some time in October 2011 I landed in Stockholm with the idea of getting on this 
voyage of the Ph.D, and today is one of those that you look back, in retrospective.

Thank Sonja and, Johan

Thank former and current colleagues/co-authors also Tomas and Polsih guy

Thank other people (Dilian, internal reviewer, opponent, examiner)

Thank former and current office mates

Thank people at department (students and faculty)

Thank parents, brother and Gabriel

Thank Joshua

Thank friends in Spain

Thank Barney


\section*{Funding}
The research leading to this thesis has been supported by the following projects:
\begin{itemize}
    \item Protection of personal information in social networks (Skydd av personlig 
    information f{\"o}r sociala n{\"a}tverk)\\
    Funded by the \ac*{ssf} grant: SSF FFL09-0086.
    % \url{http://stratresearch.se/en/research/ongoing-research/framtidens-forskningsledare-4/project/4048/}
    \item Privacy-preserving social and community networks\\
    Funded by the \ac*{vr} grant: VR 2009-3793.
    % \url{http://vrproj.vr.se/detail.asp?arendeid=69587}
\end{itemize}

We are grateful to the Swedish taxpayers for their commitment to research and development.
